What Does Reproducible Research Mean for Plant Pathology?

### 2017-04-05 What Does Reproducible Research Mean for Plant Pathology.Rmd
Update What Does Reproducible Research Mean for Plant Pathology.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, 
Toowoomba, Qld 4350, Australia
2. Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
3. Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA
Agricultural Research Service, Corvallis, OR 97330, USA
4. Zachary Foster: Horticultural Crops Research Laboratory, USDA Agricultural
Research Service, Corvallis, OR 97330, USA

@@

## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
for readers.
* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
replicate the entire study modelling the effects of climate change on rice
bacterial blight and rice leaf blast in Tanzania.
* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
* Del Ponte provides data and a reproducible report that explan in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean yied.
* Other examples from plant pathology providing e-Xtras or supplemental material

@@

### Notes
These are links to resources that may be useful for writing this or as suggested resources in the final
document that aren't easily printable for inclusion in the Dropbox folder.

https://www.r-statistics.com/2016/07/the-reproducibility-crisis-in-science-and-prospects-for-r/

https://github.com/ropensci/rrrpkg

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, Toowoomba, Qld 4350, Australia
2. Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
3. Zachary S. L. Foster: Department of Botany and Plant Pathology, ORegon State Unviersity, Corvallis, OR 97330, USA
4. Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA

@@

## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
for readers.
* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
replicate the entire study modelling the effects of climate change on rice
bacterial blight and rice leaf blast in Tanzania.
* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
* Del Ponte provides data and a reproducible report that explan in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean yied.
* Example from my lab: 
  - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI
  - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests
* Other examples from plant pathology providing e-Xtras or supplemental material

@@
